Supplement to: Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 supplement.tex
More changes

The original DSL, while inspired by the Logo~\cite{abelson1974logo} in the sense
that ones controls a moving on-off point, was designed to be congitively
plausible in the sense that some abstractions are baked in for curves and a few
structures --- it was first described in~\cite{sablemeyer2017geom}.

@@

@@

\begin{center}
\begin{tabular}{|l|l|}
  \hline Input&Output\\
  \hline\multicolumn{2}{|c|}{Double}\\
  \hline
vlxS & vlxSvlxS \\
 JkVC & JkVCJkVC \\
 dbxD & dbxDdbxD \\
 gQgB & gQgBgQgB \\
  \hline\multicolumn{2}{|c|}{Extract string delimited by ',' (inclusive),' '}\\
  \hline
LsR,uhMZI wIL & ,uhMZI  \\
 tMY,KdF hhT & ,KdF  \\
 UUPdC,UAd kCgtq & ,UAd  \\
 gQgGN,VMJ FjrXZ & ,VMJ \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to input delimited by '.'}\\
  \hline
OhCQN.DlH.LdkJ.pLh & OhDlLdpL \\
 CZr.mveZr.dvjP.YMJpg & CZmvdvYM \\
 bpub.VkkZ.dYdPr & bpVkdY \\
 zjNA.wFwY.WMMqh.OFdbr & zjwFWMOF \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to string delimited by ' ','.'}\\
  \hline
fNA YWyL.JDD & YW \\
 YWozt TPW.nczz & TP \\
 RJwiT dpW.uFU & dp \\
 FTp gNMo.JsZB & gN \\
  \hline\multicolumn{2}{|c|}{Apply strip to string delimited by ',','.'}\\
  \hline
iNEP,  GigW .Xlm & GigW \\
 xhpH,  QvwnW .mfK & QvwnW \\
 weWIC,IQjhWa .fGKz & IQjhWa \\
 xZUm, FpdE.ETcr & FpdE \\
  \hline\multicolumn{2}{|c|}{Drop first character}\\
  \hline
WYPvm & YPvm \\
 terHk & erHk \\
 asWM & sWM \\
 tBdT & BdT \\
\hline
\end{tabular}
\end{center}
  \end{comment}
\vfill

>>>>

The original DSL, while inspired by the Logo language~(\cite{abelson1974logo}) in the sense
that ones controls a moving on-off point, was designed to be congitively
plausible in the sense that some abstractions are baked in for curves and a few
structures --- it was first described in~\cite{sablemeyer2017geom}.

@@

The result presented in the main article desribe a sample of tasks and compiled
new shapes on the top row. On the bottom row is a condesed description of a run
where are displayed the mean of typical compiled programs on both sides, once
before any training and once after the last iteration --- note how the
probability weighting shaped the output space to add structure. In the middle is
the learning rate measured by holding some tasks out, training on all the other,
and with each iteration measuring the success rate on the unseen tasks. In the
given example the split was $25\%$ test and $73\%$ train.

@@

\begin{center}
\begin{tabular}{|l|l|}
  \hline Input&Output\\
  \hline\multicolumn{2}{|c|}{Double}\\
  \hline
vlxS & vlxSvlxS \\
 JkVC & JkVCJkVC \\
 dbxD & dbxDdbxD \\
 gQgB & gQgBgQgB \\
  \hline\multicolumn{2}{|c|}{Extract string delimited by ',' (inclusive),' '}\\
  \hline
LsR,uhMZI wIL & ,uhMZI  \\
 tMY,KdF hhT & ,KdF  \\
 UUPdC,UAd kCgtq & ,UAd  \\
 gQgGN,VMJ FjrXZ & ,VMJ \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to input delimited by '.'}\\
  \hline
OhCQN.DlH.LdkJ.pLh & OhDlLdpL \\
 CZr.mveZr.dvjP.YMJpg & CZmvdvYM \\
 bpub.VkkZ.dYdPr & bpVkdY \\
 zjNA.wFwY.WMMqh.OFdbr & zjwFWMOF \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to string delimited by ' ','.'}\\
  \hline
fNA YWyL.JDD & YW \\
 YWozt TPW.nczz & TP \\
 RJwiT dpW.uFU & dp \\
 FTp gNMo.JsZB & gN \\
  \hline\multicolumn{2}{|c|}{Apply strip to string delimited by ',','.'}\\
  \hline
iNEP,  GigW .Xlm & GigW \\
 xhpH,  QvwnW .mfK & QvwnW \\
 weWIC,IQjhWa .fGKz & IQjhWa \\
 xZUm, FpdE.ETcr & FpdE \\
  \hline\multicolumn{2}{|c|}{Drop first character}\\
  \hline
WYPvm & YPvm \\
 terHk & erHk \\
 asWM & sWM \\
 tBdT & BdT \\
\hline
\end{tabular}
\end{center}
\end{comment}
